---
title: "W_UP_01"
author: "Kevin B Salazar"
date: "Summer 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

We are trying to find the average number of push ups between line vs skill players. The second question is that if there a statistical difference in the average number of push ups between both positions.

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

We will be analyzing this problem using Num~Cat for the number average of push ups and categorical for the different positions. The method used will be a box plot for Graphical Descriptive Results, Numerical summary for the Numerical Descriptive Results, and finally the T-test for the inferential results.

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(pushups~position,data=mydata)
```

This graph suggest that the skill position on average does more push ups than the line position. This was taken in a two minute time period.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```

This numerical summary suggest that the skill position did about three times as much push ups on average (33 more push ups) based around the mean (49.7) than the line position's median (17.1). This was taken in a two minute time period.

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```

After conducting the T-test we get the P-value of 0.0000094211, so the P-value to so small that we have to reject the Null Hypothesis since there is a difference between the amount of push ups that the skill position and line position do in a 2 minute time period.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The original questions at hand is that if there a statistical difference in the average number of push ups between both positions. Due to the small P-value we reject the null hypothesis meaning that we have found that there is a significant difference between the number of push ups done by line position and skill position. And for the final question about the average for both positions we found the average to be 17.1 for line position and 49.7 for skill position.
